Molecular dynamics simulation of synchronization in driven particles

### 2020-12-18 manuscript/pre_draft.tex
changing tack to write an AJP not a PRE

\section{Introduction} %
%
%Outline
%------------------------------------------------------------------
%synchronization = widest audience possible
Synchronization is a universal phenomena
that can be modeled with numerical studies of confined 
driven particles.
%Christiaan Huygens 
%[has been adapted into many useful technologies...]
Examples of synchronization occur
in many biological systems with periodic behavior,
from fireflies signaling in time with a pulsed light emitting diode \cite{},
to coordinated flapping of birds wings \cite{},
to simultaneous firing of neurons in cardiac muscle \cite{}
and brain tissue \cite{}.

Huygens 1665 observation of
in-phase oscillation of pendulum clocks \cite{Pikovsky2003},
to

@@

Either coupled oscillators or a single particle on a corrugated
potential with an applied AC drive.

@@

>>>>

\section{Introduction} %
%
%Outline
%------------------------------------------------------------------
%synchronization = widest audience possible
Synchronization is a universal phenomena \cite{Pikovsky2003}.
%Christiaan Huygens 
%[has been adapted into many useful technologies...]
Huygens 1665 observation of
in-phase motions of pendulum clocks,
provides a classic example,
where two periodic oscillators
were synchronized due to
a coupling by the mounting wall \cite{Bennet2002}.
Such physical couplings are also observed
in [examples]

Biological systems benefit from cooperative
synchronzation.
Birds coordinate flapping of wings in order to [] \cite{},
to simultaneous firing of neurons in cardiac muscle \cite{}
and brain tissue \cite{}.

Such systems can be driven to form new synchronized patterns,
for instance
firefly [swarms] signal in time with a pulsed light emitting diode \cite{},
[more examples]
Driven coupled oscillations are sufficiently
broad and useful to be the subject of computational modeling.

@@

Synchronization can be modeled with numerical studies of confined 
driven particles.
Studies modeling synchronized behaviors
can be performed with
coupled oscillators []
An alternative method is to
study the dynamics of a single particle
confined in a periodic 
potential landscape subject
to with an applied driving force with constant or direct (DC)
and alterating (AC)
components.

@@

\bibitem{Bennett2002} M. Bennett, M.F. Schatz, H. Rockwood, and K. Wiesenfeld, Huygen's clocks, Proc. Roy. Soc. A 458, 563 (2002).
